Epistasis is widespread in the genetic control of transcription in humans

### 2013-05-30 docs/manuscript/nature_letter.tex
added kostya's enhancer image

We cross referenced our list of interactions with a map of chromosome interacting regions in K562 blood cell lines. Forty-nine epistatic interactions mapped to within 50kb of a chromosome interaction, and 69 mapped to within 2Mb ($p < 1.0 \times 10^{-4}$ in both cases).

- There is strong enrichment for enhancers

- There is tissue specific transcription regulation for cis SNPs - these are regulatory

- Trans SNPs are not found in tissue specific transcription regions.

@@

\begin{figure}
	\includegraphics[width=5in]{MBNL1.pdf}
	\caption{\textbf{Genotype-phenotype maps for 14 interactions controlling MBNL1} Each bar represents the mean phenotypic value for individuals in that genotype class. The rs13069559 SNP typically has a \emph{cis}-additive decreasing effect on the expression of MBNL1, but in many of these interactions the \emph{cis} effect is masked when the \emph{trans} SNP is homozygous.}
	\label{fig:mbnl13d}
\end{figure}
\clearpage

>>>>

We cross referenced our list of interactions with a map of chromosome interacting regions in K562 blood cell lines. Forty-nine epistatic interactions mapped to within 500kb of a chromosome interaction, and 69 mapped to within 2Mb ($p < 1.0 \times 10^{-4}$ in both cases, Supplementary Figure \ref{fig:chromosomeinteractions}).

There is strong enrichment for SNPs to be localised in enhancer binding regions (Supplementary Figure \ref{fig:enhancers}). This enrichment is consistent for both \emph{cis} and \emph{trans} SNPs.

@@

\begin{figure}
	\includegraphics[width=5in]{MBNL1}
	\caption{\textbf{Genotype-phenotype maps for 14 interactions controlling MBNL1} Each bar represents the mean phenotypic value for individuals in that genotype class. The rs13069559 SNP typically has a \emph{cis}-additive decreasing effect on the expression of MBNL1, but in many of these interactions the \emph{cis} effect is masked when the \emph{trans} SNP is homozygous.}
	\label{fig:mbnl13d}
\end{figure}
\clearpage

\begin{figure}
	\includegraphics[width=5in]{chromosome_interactions}
	\caption{\textbf{Number of overlaps between chromosome interactions and epistatic interactions} Interacting chromosome regions may be a possible mechanism underlying epistatic interactions. The number of epistatic interactions within 20kb, 500kb, 2Mb and 10Mb of known chromosome interacting regions are shown by red vertical lines. The histograms represent the null distribution based on random sampling of 10000 datasets for each window size.}
	\label{fig:chromosomeinteractions}
\end{figure}
\clearpage

\begin{figure}
	\includegraphics[width=5in]{enhancers}
	\caption{\textbf{There is enrichment for enhancer sequences for \emph{cis} and \emph{trans} SNPs}}
	\label{fig:enhancers}
\end{figure}
\clearpage
